Learning Excursion Sets of Vector-valued Gaussian Random Fields for Autonomous Ocean Sampling

### 2020-07-01 cover_letter/cover_letter.tex
Updated cover letter

We thank the editors and reviewers for providing feedback on our manuscript \textbf{AOAS1910-027}. The feedback have been insightful and constructive. Our response is attached along with the updated manuscript itself. We have carefully considered all the feedback in this revised version of the manuscript, which we believe is a significantly improved version of our work.

>>>>

We thank the editors and reviewers for providing feedback on our manuscript \textbf{AOAS1910-027}. The feedback have been insightful and constructive. Inspired by comments by the referees regarding the scope of the paper, we have spent substantial energy polishing its statistical character and also made an effort keeping the oceanograhic detail compact, yet sufficiently informative for the paper to be readable also by more application-driven research communities (in maritime sciences but also for instance in robotics and AI). From the statistical and mathematical side, we have tried our best to revise the formalism in such a way that further contributions can be built on top of ours, and also that we valorize some secondary findings that we have made along the way and that could be useful to researchers and practitioners from spatial statistics and beyond. This include a very modular (and conceptually appealing) way to present batch-sequential co-Kriging update formulae in heterotopic settings, generalities about excursion measures/volumes of (measurable) random fields, and also technical results towards the calculation of Stepwise Uncertainty Reduction in the vector-valued case. In particular, generalizing our former results enabled use to tackle in the revised version an arbitrary number of responses, as well as to calculate the expected excursion measure variance (on top of the expected integrated Bernoulli variance).\\

Our response is attached along with the updated manuscript itself. We have carefully considered all the feedback in this revised version of the manuscript, which we believe is a significantly improved version of our work.\\

### 2020-07-01 main_new.tex
Updated cover letter

% == Enable text degreehttps://www.overleaf.com/project/5a3268379ecbdc657d8767e8
\usepackage{textcomp}

\usepackage{amsthm,amsmath,natbib}
\RequirePackage[colorlinks,citecolor=blue,urlcolor=blue]{hyperref}

@@

\runtitle{Autonomous Oceanographic Data Collection}

@@

\subsection{Simulation Results}

@@

The case study considers the upper water column in the river plume,
represented by a two dimensional grid. Extensions to three-dimensional
domains are not methodologically different, but likely approximate
calculations by concentrating numerical integration on terms in the
vicinity of the autonomous vehicle \citep{fossum18b}. While we did not
consider any temporal effects, which would be relevant on a larger
time scale, we do consider the extension to spatio-temporal modeling
and envision that advection-diffusion equations could be useful in
such modeling
\citep{sigrist2015stochastic,richardson2017sparsity}. For more complex
oceanographic phenomena, the methods will need to be extended to
non-Gaussian phenomena, possibly feature-based mixtures of Gaussian
processes which could still be run onboard and augmented by dynamical
models. If high-resolution ocean model or satellite data are
available, it is hopefully possible to fit such more complex
statistical models. \kc{'Fit' as in modeling fit, or fit for
  augmentation with dynamical models? But also note ocean models are
  unlikely to be able to run onboard, so a simple phrase should be
  added to that effect.}

>>>>

% == Enable text 
\usepackage{textcomp}
\usepackage{amsthm,amsmath,natbib}
\RequirePackage[colorlinks,citecolor=blue,urlcolor=blue]{hyperref}

@@

\runtitle{Learning Excursion Sets for Autonomous Oceanographic Data Collection}

@@

\subsubsection{Simulation Results}

@@

The case study considers the upper water column in the river plume,
represented by a two dimensional grid. Extensions to three-dimensional
domains are not methodologically different, but likely approximate
calculations by concentrating numerical integration on terms in the
vicinity of the autonomous vehicle \citep{fossum18b}. While we did not
consider any temporal effects, which would be relevant on a larger
time scale, we do consider the extension to spatio-temporal modeling
and envision that advection-diffusion equations could be useful \citep{sigrist2015stochastic,richardson2017sparsity}. For more complex
oceanographic phenomena, the methods will need to be extended to
non-Gaussian phenomena, possibly feature-based mixtures of Gaussian
processes which could still be run onboard and augmented by dynamical
models. Running large numerical models onboard a robotic vehicle is not currently possible, but high-resolution ocean model or satellite data can be used to fit a more complex statistical model.
